Example use of prediction functions

### 2017-08-31 Hours.Rmd
updated hours

>> __Total Hours: 1...__

>>>>

8/27/2017 | 5.75 | 10:15-4:00PM | Finished with variable_setup function, started learning about the shiny app
8/27/2017 | 2.5 | 7:30-10:00PM | Continued working on the shiny app
8/28/2017 | 7.5 | 8:00-3:30PM | Worked on shiny app, met with Dr. Pileggi
8/29/2017 | 8 | 7:30-3:30PM | Added interpretations/explanations to the shiny app, met with Anthony
8/29/2017 | 2 | 5:30-7:30PM | Worked on streamlining code
8/30/2017 | 4 | 7:45-11:45AM | Continued working on code + started writing functions to fit model and get predictions 
8/30/2017 | 4 | 6:00-10:00PM | Edited documentation for functions + planned function to plot predictions
8/31/2017 |  | 8:30- | Organized code, updated hours 
>> __Total Hours: 334.58.__
